Title

### 2021-07-28 latex-slides/slides.tex
Large update to latex slides

% Metropolis Theme ---------------------------------
\usetheme{metropolis} % Use metropolis theme

@@

% --------------------------------------------------
\maketitle
% --------------------------------------------------

% --------------------------------------------------
\section{Common Items}
% --------------------------------------------------

\begin{frame}{Bullet Points \& Button}\label{main1}
    \begin{itemize}
        \item Can emphasize with \alert{the alert command}

@@

        \hyperlink{appendix1}{\beamergotobutton{Appendix}}
    \end{itemize}
\end{frame}

\begin{frame}{Citations}
    Topic 1: Spatial Frictions
    \begin{citecolor}
        [\citet{Fajgelbaum_Morales_Serrato_Zidar_2018}, \citet{Hsieh_Moretti_2019}, and \citet{Moretti_2011}]
    \end{citecolor}

    Topic 2: Blah 
    \begin{citecolor}
        [\citet{Suárez_Serrato_Zidar_2016}]
    \end{citecolor}
\end{frame}

\begin{frame}{Blocks}
    \begin{block}{Regression Specification}
        \[
            y_{it} = X_{it} \beta + \mu_i + \varepsilon_{it}
        \]
    \end{block}
\end{frame}

% --------------------------------------------------
\section{Table}
% --------------------------------------------------

\begin{frame}{Table}

    % Adjust Font Size to make table fit   
    {\fontsize{8}{10}\selectfont
    \begin{table}[!htbp] \centering 
        \caption{Regression Results} 
        \label{}

        \begin{tabularx}{\linewidth}{@{} LCC @{}} 
            \hline \hline \\
            & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
            \cline{2-3} 
            \\[-1.8ex] & (1) & (2)\\ 
            \hline \\[-1.8ex] 
            \marktopleft{ex1} Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\ 
            No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129) \markbottomright{ex1}  \\ 
            Opportunity to Learn & 0.249 (0.160) & 0.238$^{*}$ (0.139) \\ 
            Performance-Based Raises & $-$0.033 (0.202) &  \\ 
            Too Critical & 0.015 (0.147) &  \\ 
            Advancement & 11.011 (11.704) & 11.258 (7.318) \\ 
            \hline \\[-1.8ex] 
            Observations & 30 & 30 \\ 
            R$^{2}$ & 0.715 & 0.715 \\ 
            Adjusted R$^{2}$ & 0.656 & 0.682 \\ 
            \hline \hline

            \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
        \end{tabularx} 
    \end{table}
    }

@@

% --------------------------------------------------
\section{Figures}
% --------------------------------------------------

% 4:3 ratio or else it will have white space
\imageframe{img/kanagawa.jpg}

% Use 4:3 ratio for figures
\begin{frame}{Figure}
    \begin{center}
        \includegraphics[width= .95\linewidth]{img/kanagawa.jpg}
    \end{center}
\end{frame}

\begin{frame}{Figure with comments}
    \begin{columns}[T] % align columns
    \begin{column}{.62\textwidth}
        \includegraphics[width= \linewidth]{img/kanagawa.jpg}
    \end{column}%

    \begin{column}{.38\textwidth}
        % Horizontal Bar
        {\color{accent}\rule{\linewidth}{3pt}}

        \begin{itemize}[leftmargin=0cm]
            \item Point 1 about the figure to the left. This really only works for 16:9 aspect ratio
            \item Point 2
        \end{itemize}
    \end{column}%
    \end{columns}
\end{frame}

\begin{frame}{Two Columns general}
    \begin{columns}[T] % T = vertical align columns at the top
    \begin{column}{.50\textwidth}
        {\color{accent}\rule{\linewidth}{3pt}}
        Column 1
    \end{column}

    \begin{column}{.50\textwidth}
        {\color{accent}\rule{\linewidth}{3pt}}
        Column 2
    \end{column}
    \end{columns}
\end{frame}

% --------------------------------------------------
\begin{frame}[allowframebreaks]{References}
    \printbibliography
\end{frame}
% --------------------------------------------------

% --------------------------------------------------
\appendix
% --------------------------------------------------

@@

    % Adjust Font Size to make table fit
    {\fontsize{9}{10}\selectfont

        \begin{table}
            \centering 
            \caption{Summary Statistics}
            \label{appendix_summ_stat}

            \begin{tabularx}{\linewidth}{@{} LCCCCCCC @{}} 
                \hline 
                \hline \\[-1.8ex] 
                Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
                \hline \\[-1.8ex] 
                rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
                complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
                privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
                learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
                raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
                critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
                advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
                \hline \\

                \multicolumn{8}{p{.8\textwidth}}{\textit{Notes:} Using R base dataframe attitude}
            \end{tabularx}

        \end{table}

    }

>>>>

@@

% ------------------------------------------------------------------------------
\maketitle
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\section{Common Items}
% ------------------------------------------------------------------------------

\begin{frame}{Components}{Bullet Points \& Button}\label{main1}
    This section highlights commonly used components and their theming

    \begin{itemize}
        \item Can emphasize with \alert{the alert command}

@@

        \vspace{5mm}
        \hyperlink{appendix1}{\beamergotobutton{Appendix}}
    \end{itemize}
\end{frame}

\begin{frame}{Components}{Numbered Lists}
    You can also use numbered items that look a bit more professional

    \begin{enumerate}
        \item Pretty good

        \item To include things in appendix
    \end{enumerate}
\end{frame}

\begin{frame}{Components}{Citations}
    Topic 1: Spatial Frictions
    \begin{citecolor}
        [\citet{Fajgelbaum_Morales_Serrato_Zidar_2018}, \citet{Hsieh_Moretti_2019}, and \citet{Moretti_2011}]
    \end{citecolor}

    \vspace{5mm}
    Topic 2: Blah 
    \begin{citecolor}
        [\citet{Suárez_Serrato_Zidar_2016}]
    \end{citecolor}
\end{frame}

\begin{frame}{Components}{Blocks}
    \begin{block}{Regression Specification}
        The main specificaiton is as follows:

        \[
            y_{it} = X_{it} \beta + \mu_i + \varepsilon_{it}
        \]
    \end{block}
\end{frame}

\begin{frame}{Components}{Colors}
    {\color{navy} Test sentence with \textbackslash color\{navy\}}\newline
    {\color{kelly} Test sentence with \textbackslash color\{kelly\}}\newline
    {\color{ruby} Test sentence with \textbackslash color\{ruby\}}\newline
    {\color{alice} Test sentence with \textbackslash color\{alice\}}\newline
    {\color{daisy} Test sentence with \textbackslash color\{daisy\}}\newline
    {\color{coral} Test sentence with \textbackslash color\{coral\}}\newline
    {\color{jet} Test sentence with \textbackslash color\{jet\}}\newline
    {\color{asher} Test sentence with \textbackslash color\{asher\}}\newline
\end{frame}

\begin{frame}{Components}{Two Columns general}
    \begin{columns}[T] % T = vertical align columns at the top
    \begin{column}{.50\textwidth}
        {\color{accent}\rule{\linewidth}{2pt}}
        Column 1

        \begin{enumerate}
            \item Bullet points for this column that can go over lines
            \item b
            \item c
        \end{enumerate}
    \end{column}

    \begin{column}{.50\textwidth}
        {\color{accent}\rule{\linewidth}{2pt}}
        Column 2

        \begin{enumerate}
            \item a
            \item b
            \item c
        \end{enumerate}
    \end{column}
    \end{columns}
\end{frame}

\begin{frame}{Components}{Example of tikz figure}

\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=1.5cm]
    % nodes %
    \node[text centered] (d) {$D$};
    \node[below right of = d, text centered] (x) [draw, shape=circle, line width = 1] {$X$};
    \node[above right of = x, text centered] (y) {$Y$};
    \node[below of = x, text centered, purple] (z) {$Z$};

    % edges %
    \path[->, line width= 1] 
        (d) edge (y)
        (x) edge (d)
        (x) edge (y);
    \path[->, line width= 1, purple]
        (z) edge [out=135, in=260, looseness=0.5] node[left, black] {$\text{Good variation in D}$} (d)
        (z) edge [out=45, in=280, looseness=0.5] (y);
\end{tikzpicture}
\end{center}
\end{figure}

@@

% ------------------------------------------------------------------------------
\section{Table}
% ------------------------------------------------------------------------------

\begin{frame}

% Adjust Font Size to make table fit   
\begin{table}[!htbp]
    \caption{Regression Results} 
    \label{}

    \begin{adjustbox}{max width = \textwidth, width = 0.75\textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} lcc @{}} 
                \toprule
                & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
                \cline{2-3} \\
                & (1) & (2)\\ 
                \midrule

                \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \markbottomright{ex1} \\ 
                No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129)  \\ 
                Opportunity to Learn & 0.249 (0.160) & 0.238$^{*}$ (0.139) \\ 
                Performance-Based Raises & $-$0.033 (0.202) &  \\ 
                Too Critical & 0.015 (0.147) &  \\ 
                Advancement & 11.011 (11.704) & 11.258 (7.318) \\ 
                \hline \\[-1.8ex] 
                Observations & 30 & 30 \\ 
                R$^{2}$ & 0.715 & 0.715 \\ 
                \bottomrule

            \end{tabular} 
            % Notes 
            \begin{tablenotes}
                \item \textit{Notes.} $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01.
            \end{tablenotes}
        \end{threeparttable}
    \end{adjustbox}
\end{table}
\end{frame}

% ------------------------------------------------------------------------------
\section{Figures}
% ------------------------------------------------------------------------------

% 4:3 ratio for figures
% or else it will have white space
\imageframe{img/kanagawa.jpg}

\begin{frame}{Figure}{}
    \begin{center}
        \resizebox{0.9\columnwidth}{!}{%
            \includegraphics{img/kanagawa.jpg}
        }
    \end{center}
\end{frame}

% ------------------------------------------------------------------------------
\begin{frame}[allowframebreaks]{References}
    \printbibliography
\end{frame}
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\appendix
% ------------------------------------------------------------------------------

@@

\begin{table}
    \caption{Summary Statistics}
    \label{appendix_summ_stat}
    \begin{adjustbox}{max width = \textwidth, width = 0.8 \textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} lccccccc @{}} 
                \toprule
                Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
                \hline \\[-1.8ex] 
                rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
                complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
                privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
                learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
                raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
                critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
                advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
                \bottomrule
            \end{tabular} 
            % Notes 
            \begin{tablenotes}
                \item \textit{Notes.} Using R base dataframe attitude.
            \end{tablenotes}
        \end{threeparttable}
    \end{adjustbox}
\end{table}
